Demystifying the Dynamic Slicing and SFL Combination

### 2019-02-12 paper/ijcai/paper.tex
stop here. check if these metrics make sense.

\Mar{parei aqui}

@@

Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

As in other recent related studies, we used the \dfj{} benchmark in
our experiments~\cite{just-defects4j-issta2014}. The \dfj{} benchmark
includes six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111751  & 6057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306276  & 26797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149521  & 27930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230159  & 8458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141610  & 3289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22787  & 8835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
\label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Methodology}\label{sec:methodology}

The main goal of our evaluation is to understand what is the impact of \ds{} on 
\sfl{} after minimizing the $k$ highest faulty source files which comprise the highest faulty statements. Firstly, we ran the dataset presented in Section~\ref{sec:analysis} with \sfl{} to 
gather the coverage statements ordered from the highest faulty statement to the
lowest faulty statement. This list is the input of the \comb{} technique. For each defect, the list is evaluated in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source files. Then, Lithium minimizes each source file for each testcase of the defect considering the top-$5$ (\comb{}-$5$) and top-$10$ (\comb{}-$10$) of source files separately. Some defects have more than one testcase. In the end, we update spectra $S$ based on the output of the minimization as presented in Figure~\ref{fig:ds-reduction} to obtain the faulty statements ranking after minimization. All scripts used to run these experiments and gather data are available at \url{TBA} and \url{TBA}, respectively.

We perform experiments for \comb{}-$5$ and \comb{}-$10$. These techniques results are analyzed against \sfl{}. The difference in the diagnostic effort is measured
using

\begin{equation}
    \Delta{}C = C(\textrm{SFL}) - C(\textrm{SFL+DS-k})
\end{equation}

@@

\Sof{Parei Aqui}

>>>>

@@

\Mar{I left a bunch o comments to Sofia on hangouts...$\rightarrow$}
Lithium takes as input a function of interest that can be designed according to the problem to be solved. The function of interest determines if the test case output is interesting or not. In this study, interesting means that the test execution path is equal to the expected one. This information can be deducted from the defects stack traces which show the stack of functions called until the thrown of an exception. The interesting function compares both stack traces (from the test under evaluation and the expected one) until the call where the test fails. For each chunk under evaluation, the test is executed after the chunk being deleted from the source code (Algorithm \ref{alg:finc}, line 2). Both test ($testStk$) and expected ($expStk$) stack traces are filtered. We only consider stack traces until the line where the main exception is launched. These operations are performed by line 3 and 4 from Algorithm 2. Finally, both messages are compared and if equal the chunk will be deleted from the project, i.e., the chunk is not interesting to reveal the fault of the test.

@@

We used the \dfj{} benchmark in our
experiments~\cite{just-defects4j-issta2014}. This benchmark includes
six different subjects and \numFaults{} faults (Table \ref{tab:df4j}).
\lang{} is a library that provides a set of helper utilities for the
     {\small\texttt{java.lang}} API. \cmath{} is a lightweight library
     of self-contained mathematics and statistics components. The
     \closure{} is a toolset for turning JavaScript files into smaller
     scripts for faster download and execution in the
     browser. \chart{} is a Java library for creating charts. \jtime{}
     is a lightweight library that aims to replace the default Java
     {\small\texttt{java.util.Date}} classes providing simpler
     APIs. \mockito{} is a mocking testing framework.

\newcommand{\cgray}[1]{\cellcolor{gray!25}#1}
\begin{table}[h]
  \centering
  \setlength{\tabcolsep}{4pt}
    \begin{tabular}{lrrr}
      \toprule
      Project            & Size (LOC) & \# Tests & \# Faults \\ %\comments{& Failing Test Cases &}
      \midrule
      \lang{}            & 111,751  & 6,057 & 65       \\   %\commentst{& 124   &  -}\\
      \cmath{}           & 306,276  & 26,797 & 106     \\   %\comments{& 177   &  -}\\
      \closure{}         & 149,521  & 27,930  & 133     \\   %\comments{& 350   &  -}\\
      \chart{}           & 230,159  & 8,458 & 26      \\  %\comments{& 92    &  -}\\
      \jtime{}           & 141,610  & 3,289 & 27       \\   %\comments{& 76    &  -}\\
      \mockito{}         & 22,787  & 8,835 & 38    \\     %\comments{& 118   &  -}\\
      \bottomrule
  \end{tabular}
\caption {Characterization of \dfj{} subjects.\Sof{Use SLOCCount to count size}}
\label{tab:df4j}
\end{table}
\normalsize

@@

\subsection{Experimental Methodology}\label{sec:methodology}

%% The main goal of our evaluation is to understand what is the impact of
%% \ds{} on \sfl{} after minimizing the $k$ highest faulty source files
%% which comprise the highest faulty statements.

Recall from Section~\ref{sec:combination} that the \comb{} combination
takes on input a value denoting the $k$ most suspicious distinct
files. To evaluate the effectiveness of \comb{}, we compared its
performance with \sfl{} for each defect on each subject program from
the dataset, for $k\in\{5,10\}$. These files are obtained directly
from the ranking. We refer to these variations as \combpar{k}. We
compared \combpar{5} and \combpar{10} against \sfl{} using the
following metrics.\Mar{Sofia, I don't see a reason for an equation to
  only show the difference of cost. Please describe precisely the
  metrics. In this case, I can't find what C stands for. Also,
 you need to describe precisely what top@n (or someother name) means
 in this context. Check if it makes sense for SFL.$\rightarrow$}

\begin{equation}
    \Delta{}C = C(\textrm{SFL}) - C(\textrm{\combpar{k}})
\end{equation}

@@

%% Firstly, we ran the dataset presented in Section~\ref{sec:analysis}
%% with \sfl{} to gather the coverage statements ordered from the highest
%% faulty statement to the lowest faulty statement. This list is the
%% input of the \comb{} technique. For each defect, the list is evaluated
%% in order to get the top-$k$, for $k\in\{5,10\}$, of suspicious source
%% files. Then, Lithium minimizes each source file for each testcase of
%% the defect considering the top-$5$ (\comb{}-$5$) and top-$10$
%% (\comb{}-$10$) of source files separately. Some defects have more than
%% one testcase. In the end, we update spectra $S$ based on the output of
%% the minimization as presented in Figure~\ref{fig:ds-reduction} to
%% obtain the faulty statements ranking after minimization. All scripts
%% used to run these experiments and gather data are available at
%% \url{TBA} and \url{TBA}, respectively.

%% \Sof{Parei Aqui}
